%--------------------------------------------------
% Resume in LaTeX – Karneeshkar V
% Template adapted from: https://github.com/sb2nov/resume
% License: MIT
%--------------------------------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%------------- Page Geometry -----------------------
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%------------- Section Heading ---------------------
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine-readable / ATS parsable
\pdfgentounicode=1

%------------- Custom Commands ---------------------
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%===================================================
%%%%%%             RESUME STARTS               %%%%%%
%===================================================

\begin{document}

%------------------ NAME & CONTACT -----------------
\begin{center}
  \textbf{\Huge \scshape Karneeshkar V} \\ \vspace{1pt}
  \small +91 99109 77193 $|$ 
  \href{mailto:karneeshkar68@gmail.com}{\underline{karneeshkar68@gmail.com}} $|$
  \href{https://www.linkedin.com/in/karneeshkar-velmurugan/}{\underline{linkedin.com/in/karneeshkar-velmurugan}} $|$
  \href{https://github.com/KarneeshkarV}{\underline{github.com/KarneeshkarV}} 
\newline \newline
\href{https://karneeshkar.tech/}{\underline{Portfolio}  }$|$
\href{https://www.karneeshkar.tech/#terminal}{\underline{Terminal portfolio}}
\end{center}

%------------------ SUMMARY ------------------------
\section{Professional Summary}
AI engineer focused on building, fine-tuning, and shipping LLM‑powered products. Hands-on with LLaMA 3.1 fine‑tuning, agentic workflows, retrieval, and MLOps; strong backend foundation in Python/FastAPI and cloud deployment. Track record of shipping measurable impact—e.g., 88\% intent classification in production chatbots and 94\% vision accuracy on edge devices—and leading cross‑functional teams to reliable releases.

%------------------ TECHNICAL SKILLS ---------------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{:  Python, Bash, Go, SQL, C/C++} \\
    \textbf{AI \& Data}{: PyTorch, TensorFlow, Computer Vision, Sensor Data Processing} \\
    \textbf{Web \& Cloud}{: FastAPI, Node.js, REST APIs, llama.cpp, AWS, Docker, Git} \\
    \textbf{Databases}{: PostgreSQL, SQLite, MongoDB}\\
              \textbf{Soft skills}{: Communication, Teamwork, Active listening, Problem solving, Critical thinking, Time management } }}
  }}
\end{itemize}

%------------------ EXPERIENCE ---------------------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Tech Lead}{Jun 2025 –  Current}
    {2Cents Capital}{Bengaluru, India}
    \resumeItemListStart
      \resumeItem{Led and scaled cross-functional Mobile and AI teams (10+ engineers) to deliver high-impact features with 95\% on-time release rate.}
      \resumeItem{Published a fully responsive investment application on both iOS App Store and Google Play, achieving $<$0.5s cold-start time.}
      \resumeItem{Designed and deployed AI agents across the end-to-end customer journey—including customer support, onboarding, and market research—improving support resolution speed by 40\% and reducing manual intervention costs by 30\%.}
    \resumeItemListEnd

  \resumeSubheading
    {Software Developer}{Jan 2025 -- Jun 2025}
    {Visteon}{Chennai, India}
    \resumeItemListStart
      \resumeItem{Created diagnostic routines for JLR platforms that detect system anomalies with \(96\%\) accuracy, boosting vehicle reliability.}
      \resumeItem{Optimized real-time dashboard software (SomeIP on QNX/Linux) in C, reducing processing latency by \(25\%\).}
      \resumeItem{Wrote unit and functional tests to reach \(99.8\%\) code coverage across the code-base with zero deviations.}
    \resumeItemListEnd

  \resumeSubheading
    {Automation Intern}{Dec 2024 -- Jan 2025}
    {Procter \& Gamble}{Hyderabad, India}
    \resumeItemListStart
      \resumeItem{Implemented IIoT monitoring on five production lines, ingesting \(2\text{M}\,\)+ data points daily with \(99.9\%\) uptime.}
      \resumeItem{Automated quality-control workflows, cutting manual inspection time \(40\%\) and improving defect detection \(15\%\).}
    \resumeItemListEnd

  \resumeSubheading
    {IoT \& LoRaWAN Developer}{May 2024 -- Jun 2024}
    {Tynatech Ingenious Pvt Ltd}{Noida, India}
    \resumeItemListStart
      \resumeItem{Built RESTful APIs / webhooks connecting \(50+\) LoRaWAN devices to cloud platforms.}
      \resumeItem{Optimized UART–LoRaWAN interface to raise throughput \(30\%\) via efficient buffer management.}
      \resumeItem{Added MQTT streaming for real-time gateway visualization, handling \(100+\) msgs s\(^{-1}\).}
    \resumeItemListEnd

  \resumeSubheading
    {Web Development Intern}{Oct 2023 -- Dec 2023}
    {Intellect Design Arena}{Chennai, India}
    \resumeItemListStart
      \resumeItem{Developed PHP-based financial portals with \(30\%\) faster page loads.}
      \resumeItem{Managed cloud infra for five web apps, configuring auto-scaling for \(99.9\%\) availability.}
      \resumeItem{Created analytics dashboards delivering real-time engagement and conversion insights.}
    \resumeItemListEnd

  \resumeSubheading
    {R\&D Intern}{Aug 2023 -- Sep 2023}
    {Hindustan Aeronautics Ltd (HAL)}{Bangalore, India}
    \resumeItemListStart
      \resumeItem{Optimised autopilot algorithms, cutting computational overhead \(22\%\) while meeting safety constraints.}
      \resumeItem{Authored C++ simulation tool covering \(200+\) control-system test scenarios.}
      \resumeItem{Assisted avionics teams with system documentation and verification protocols.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%------------------ PROJECTS -----------------------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
    {\textbf{Full‑Stack AI Personal Assistant}
    \( | \) \emph{Go, Google A2A, PostgreSQL, React}}
    {Dec 2024}
\resumeItemListStart
      \resumeItem{Engineered and deployed a cloud assistant that centralizes and automates personal workflows.}
      \resumeItem{Built asynchronous agents to orchestrate complex Google Workspace operations (mail, calendar, docs).}
      \resumeItem{Modeled a personal knowledge graph to ground answers and personalize actions.}
    \resumeItemListEnd
  \resumeProjectHeading
    {\textbf{LLaMA 3.1 Fine‑Tuning for Code Reasoning}
      \( | \) \emph{Python, RL (GPRO), Hugging Face}}{Apr 2025}
    \resumeItemListStart
      \resumeItem{Fine‑tuned LLaMA‑3.1 8B on a paired‑coding dataset (\href{https://huggingface.co/datasets/Advaith1612/paired-coding}{link}) using a single H100 to boost code reasoning.}
      \resumeItem{Applied GPRO reinforcement learning with Gemma 3 as a reward model (inspired by DeepSeek‑R1).}
      \resumeItem{Improved pass@1 by \textasciitilde15\% on a custom eval and averaged +10\% on public coding benchmarks.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Instagram Automation Bot}
      \( | \) \emph{Python, FastAPI, Redis, AWS}}{Dec 2024}
    \resumeItemListStart
      \resumeItem{Deployed cloud bot handling \(1000+\) daily interactions with \(99.5\%\) uptime.}
      \resumeItem{Added LLM‑based sentiment/intent detection achieving \(88\%\) accuracy in production.}
      \resumeItem{Introduced Redis caching to cut Meta Graph API calls \(65\%\); p50 response \(<\) 500\,ms.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Multipurpose VR Gloves with Gesture Recognition}
      \( | \) \emph{Unity, C\#, ESP32, ML}}{Sep 2024}
    \resumeItemListStart
      \resumeItem{Built VR gloves capturing \(15+\) gestures at \(92\%\) accuracy using flex-sensor ML pipelines.}
      \resumeItem{Developed web UI for mapping gestures to \(20+\) system commands; integrated Unity for gaming/assistive control.}
    \resumeItemListEnd


  \resumeProjectHeading
    {\textbf{Embedded Athlete-Performance Monitoring System}
      \( | \) \emph{ESP32, PyTorch, OpenCV}}{Mar 2024}
    \resumeItemListStart
      \resumeItem{Ran edge CV on ESP32 to analyze runner form in real time; fused MPU6050, VO\(_2\), and temperature signals.}
      \resumeItem{Built a decision‑tree classifier with a Flask/Plotly dashboard for actionable feedback.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Smart Rhesus Macaque Deterrent System}
      \( | \) \emph{Jetson Nano, CV, Ultrasonic}}{Mar 2024}
    \resumeItemListStart
      \resumeItem{Achieved \(93\text{--}94\%\) macaque detection across varied lighting; ultrasonic emitters cut intrusions \(90\%\).}
      \resumeItem{Designed a robust CV pipeline (tracking + classification) optimized for low‑power edge deployment.}
    \resumeItemListEnd



\resumeSubHeadingListEnd

%------------------ EDUCATION ----------------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Vellore Institute of Technology}{Chennai, India}
    {B.Tech. Electronics \& Computer Engineering; GPA: 8.66/10}{2021 -- 2025}
\resumeSubHeadingListEnd

%--------------------------------------------------
\end{document}
