%--------------------------------------------------
% Resume in LaTeX - Karneeshkar V
% Template adapted from: https://github.com/sb2nov/resume
% License: MIT
%--------------------------------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage{amsmath}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%------------- Page Geometry -----------------------
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%------------- Section Heading ---------------------
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine-readable / ATS parsable
\pdfgentounicode=1

%------------- Custom Commands ---------------------
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%===================================================
%%%%%%             RESUME STARTS               %%%%%%
%===================================================

\begin{document}

%------------------ NAME & CONTACT -----------------
\begin{center}
  \textbf{\Huge \scshape Karneeshkar V} \\ \vspace{1pt}
  \small +91 99109 77193 $|$ 
  \href{mailto:karneeshkar68@gmail.com}{\underline{karneeshkar68@gmail.com}} $|$
  \href{https://www.linkedin.com/in/karneeshkar-velmurugan/}{\underline{linkedin.com/karneeshkar-velmurugan}} $|$
  \href{https://github.com/KarneeshkarV}{\underline{github.com/KarneeshkarV}} 
  \newline \newline
  \href{https://karneeshkar.tech/}{\underline{Portfolio}}
\end{center}

%------------------ SUMMARY ------------------------
\section{Professional Summary}
Cross-domain engineer with production experience spanning Full-Stack Development (Python, Node.js, Go, SQL, AWS), Generative AI (LLMs, RAG, multi-agent systems), and Embedded/IoT (C/C++, Rust, RTOS on STM32/ESP32). Proven track record of leading engineering teams, architecting zero-to-production products, and bridging real-time hardware with cloud-scale AI services. Passionate about applied ML research and building intelligent, high-reliability systems at scale.

%------------------ TECHNICAL SKILLS ---------------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: Rust, C/C++, Python, Go, Bash, PHP, JavaScript/TypeScript, SQL} \\
    \textbf{Embedded \& IoT}{: Zephyr RTOS, Espressif IDF, STM32, ESP32, Arduino, Raspberry Pi, LoRaWAN, MQTT} \\
    \textbf{AI \& ML}{: PyTorch, TensorFlow, RLHF/GRPO, RAG, LLM Fine-Tuning, Computer Vision, Sensor Fusion} \\
    \textbf{Web \& Cloud}{: React Native, Next.js, Flask, Node.js, REST APIs, AWS, Docker, CI/CD, Git} \\
    \textbf{Databases}{: PostgreSQL, MySQL, SQLite, MongoDB, Redis} \\
    \textbf{Leadership}{: Cross-functional team leadership, Agile/Scrum, Technical architecture, Code review, Mentorship} }}
\end{itemize}

%------------------ EXPERIENCE ---------------------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
  {Software Developer 2 --- Tech Lead}{Jul 2025 -- Present}
  {2Cents Capital}{Bengaluru, India}
  \resumeItemListStart
    \resumeItem{Founding engineer and tech lead orchestrating Mobile, AI, and Quantitative Finance verticals --- instrumental in defining the product architecture and engineering culture from inception.}
    \resumeItem{Architected and delivered Valura AI (iOS + Android), a production-grade AI-powered investment platform, end-to-end --- achieving sub-500\,ms cold-start latency and a 4.8-star App Store rating.}
    \resumeItem{Led cross-functional engineering teams of 10+ across mobile and AI; instituted agile delivery practices yielding a 95\% on-time release cadence.}
    \resumeItem{Designed and operationalized a multi-agent AI orchestration layer spanning onboarding, customer support, and market intelligence --- reducing manual support burden by 40\% and operational expenditure by 30\%.}
    \resumeItem{Engineered algorithmic trading infrastructure integrating real-time market signal ingestion, strategy backtesting frameworks, and automated order execution pipelines.}
    \resumeItem{Architected real-time market-data streaming pipelines and a portfolio analytics engine delivering personalized investment insights to thousands of concurrent users.}
    \resumeItem{Instituted CI/CD pipelines, automated regression frameworks, and observability dashboards, driving a 60\% reduction in post-release defect density.}
  \resumeItemListEnd

  \resumeSubheading
    {Software Developer Intern}{Jan 2025--Jun 2025}
    {Visteon}{Chennai, India}
    \resumeItemListStart
      \resumeItem{Engineered diagnostic routines for Jaguar Land Rover platforms achieving 96\% anomaly detection accuracy; optimized SOME/IP service-oriented middleware in C, yielding a 25\% latency reduction.}
      \resumeItem{Attained 99.8\% unit-test coverage across safety-critical codepaths with zero ASIL deviations.}
    \resumeItemListEnd

  \resumeSubheading
    {Automation Intern}{Dec 2024--Jan 2025}
    {Procter \& Gamble}{Hyderabad, India}
    \resumeItemListStart
      \resumeItem{Deployed Industrial IoT telemetry infrastructure across 5 manufacturing lines, ingesting 2M+ daily data points at 99.9\% availability --- eliminating 40\% of manual inspection overhead.}
    \resumeItemListEnd

  \resumeSubheading
    {IoT \& LoRaWAN Developer}{May 2024--Jun 2024}
    {Tynatech Ingenious Pvt Ltd}{Noida, India}
    \resumeItemListStart
      \resumeItem{Developed RESTful API gateway integrating 50+ LoRaWAN edge devices with cloud infrastructure; optimized UART transport layer for 30\% throughput improvement and implemented MQTT streaming sustaining 100+ msg/s.}
    \resumeItemListEnd

  \resumeSubheading
    {Web Development Intern}{Oct 2023--Dec 2023}
    {Intellect Design Arena}{Chennai, India}
    \resumeItemListStart
      \resumeItem{Developed enterprise financial portals in PHP delivering 30\% page-load improvement; administered cloud infrastructure for 5 production applications at 99.9\% availability with integrated analytics dashboards.}
    \resumeItemListEnd

  \resumeSubheading
    {R\&D Intern}{Aug 2023--Sep 2023}
    {Hindustan Aeronautics Ltd (HAL)}{Bangalore, India}
    \resumeItemListStart
      \resumeItem{Optimized flight autopilot control algorithms reducing computational overhead by 22\%; developed a C++ simulation framework encompassing 200+ control-system verification scenarios.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%------------------ PROJECTS -----------------------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Level2 -- Cross-Platform Gym Management App}
      \( | \) \emph{React Native, Go, AWS, iOS, Android}}{2025}
    \resumeItemListStart
      \resumeItem{Designed and shipped Level2, a production gym management platform live on iOS App Store and Google Play --- featuring workout tracking, member lifecycle management, and intelligent scheduling.}
      \resumeItem{Engineered event-driven real-time synchronization architecture ensuring sub-second data consistency across distributed mobile clients.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Naar -- Full-Stack Restaurant Platform}
      \( | \) \emph{Next.js, Node.js, PostgreSQL, AWS}}{2025}
    \resumeItemListStart
      \resumeItem{Delivered a production restaurant operations platform (\href{https://naarkuwait.com/en}{naarkuwait.com}) encompassing admin dashboard, kitchen display system, and customer-facing ordering interface --- achieving 50\% reduction in order processing latency.}
      \resumeItem{Architected granular role-based access control and a real-time order orchestration pipeline supporting concurrent multi-interface sessions.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{LLaMA 3.1 Fine-Tuning for Code Reasoning --- Applied ML Research}
      \( | \) \emph{Python, GRPO, Hugging Face, PyTorch}}{Apr 2025}
    \resumeItemListStart
      \resumeItem{Conducted applied research on reinforcement learning from human feedback (RLHF) for code generation, fine-tuning LLaMA-3.1 8B on a curated paired-coding corpus (\href{https://huggingface.co/datasets/Advaith1612/paired-coding}{dataset}).}
      \resumeItem{Implemented Group Relative Policy Optimization (GRPO) with Gemma 3 as the reward model, drawing on DeepSeek-R1 methodology to enhance chain-of-thought reasoning in code synthesis tasks.}
      \resumeItem{Demonstrated \textasciitilde15\% pass@1 improvement on custom evaluation benchmarks and +10\% average uplift across established public coding benchmarks.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Instagram Automation Bot}
      \( | \) \emph{Python, FastAPI, Redis, AWS}}{Dec 2024}
    \resumeItemListStart
      \resumeItem{Deployed a cloud-native automation service processing \(1000+\) daily interactions at \(99.5\%\) availability.}
      \resumeItem{Integrated LLM-driven sentiment analysis and intent classification pipeline achieving \(88\%\) production accuracy.}
      \resumeItem{Implemented Redis-backed caching layer reducing Meta Graph API invocations by \(65\%\); sustained p50 latency below 500\,ms.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Multipurpose VR Gloves with Gesture Recognition}
      \( | \) \emph{Unity, C\#, ESP32, ML}}{Sep 2024}
    \resumeItemListStart
      \resumeItem{Engineered VR gloves with ML-driven gesture classification capturing \(15+\) gestures at \(92\%\) recognition accuracy via flex-sensor signal processing pipelines.}
      \resumeItem{Developed a configuration interface mapping gestures to \(20+\) system commands; integrated Unity runtime for gaming and assistive technology applications.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{RAK Gateway Configurator}
      \( | \) \emph{Python, Flask, SQL, Bash}}{Jun 2024}
    \resumeItemListStart
      \resumeItem{Developed a full-stack provisioning tool streamlining configuration workflows for RAKwireless LoRaWAN gateways, reducing network administrator setup time.}
      \resumeItem{Automated device discovery, credential lifecycle management, and over-the-air firmware upgrade orchestration.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Embedded Athlete-Performance Monitoring System}
      \( | \) \emph{ESP32, PyTorch, OpenCV}}{Mar 2024}
    \resumeItemListStart
      \resumeItem{Deployed edge computer vision inference on ESP32 for real-time biomechanical analysis; implemented multi-sensor fusion (MPU6050 IMU, VO\(_2\) max, thermistor) pipeline.}
      \resumeItem{Trained a decision-tree ensemble classifier and built a Flask/Plotly analytics dashboard delivering actionable performance feedback.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Smart Rhesus Macaque Deterrent System}
      \( | \) \emph{Jetson Nano, CV, Ultrasonic}}{Mar 2024}
    \resumeItemListStart
      \resumeItem{Achieved \(94\%\) detection accuracy under variable illumination conditions; ultrasonic deterrent subsystem reduced intrusion events by \(90\%\).}
      \resumeItem{Designed power-management firmware reducing energy consumption by \(35\%\), enabling autonomous solar-powered field deployment.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Wearable Jump-Height Measurement Device}
      \( | \) \emph{ESP32, MPU6050, Flask}}{Mar 2024}
    \resumeItemListStart
      \resumeItem{Developed ankle-mounted inertial measurement device achieving \(\pm1\,\text{cm}\) accuracy validated against laboratory force-plate ground truth.}
      \resumeItem{Implemented extended Kalman filter suppressing sensor noise by \(80\%\); built SQLite-backed Flask analytics dashboard for longitudinal performance tracking.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{RFID-based Runner Tracking System}
      \( | \) \emph{Industrial RFID, PHP, Raspberry Pi}}{Dec 2023}
    \resumeItemListStart
      \resumeItem{Automated precision timing for \(5\,\text{km}\) athletic training events using industrial UHF RFID readers.}
      \resumeItem{Developed web-based record management interface with seamless legacy-system data integration.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%------------------ EDUCATION ----------------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Vellore Institute of Technology}{Chennai, India}
    {B.Tech. Electronics \& Computer Engineering; GPA: 8.66/10}{2021--2025}
  \resumeSubheading
    {NISM -- National Institute of Securities Markets}{India}
    {NISM Series VA: Mutual Fund Distributors Certification}{2025}
\resumeSubHeadingListEnd

%--------------------------------------------------
\end{document}
