%--------------------------------------------------
% Resume in LaTeX – Karneeshkar V
% Template adapted from: https://github.com/sb2nov/resume
% License: MIT
%--------------------------------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%------------- Page Geometry -----------------------
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%------------- Section Heading ---------------------
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine-readable / ATS parsable
\pdfgentounicode=1

%------------- Custom Commands ---------------------
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%===================================================
%%%%%%             RESUME STARTS               %%%%%%
%===================================================

\begin{document}

%------------------ NAME & CONTACT -----------------
\begin{center}
  \textbf{\Huge \scshape Karneeshkar V} \\ \vspace{1pt}
  \small +91 99109 77193 $|$ 
  \href{mailto:karneeshkar68@gmail.com}{\underline{karneeshkar68@gmail.com}} $|$
  \href{https://www.linkedin.com/in/karneeshkar-velmurugan/}{\underline{linkedin.com/in/karneeshkar-velmurugan}} $|$
  \href{https://github.com/KarneeshkarV}{\underline{github.com/KarneeshkarV}} 
\newline \newline
\href{https://karneeshkar.tech/}{\underline{Portfolio}  }$|$
\href{https://www.karneeshkar.tech/#terminal}{\underline{Terminal portfolio}}
\end{center}

%------------------ SUMMARY ------------------------
\section{Professional Summary}
Mobile developer specializing in React Native, with proven experience shipping high‑performance cross‑platform apps to iOS App Store and Google Play. Expert in TypeScript/JavaScript, mobile architecture patterns, and optimization techniques. Strong track record of leading mobile teams, delivering production apps with sub‑second cold‑start times, and integrating native modules for platform‑specific features.

%------------------ TECHNICAL SKILLS ---------------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Mobile}{: React Native, Expo, TypeScript, JavaScript, React, React Navigation, Native Modules} \\
    \textbf{State \& Data}{: Redux, Zustand, React Query, AsyncStorage, MMKV, SQLite, PostgreSQL, REST APIs} \\
    \textbf{Testing \& Quality}{: Jest, React Native Testing Library, Detox, ESLint, TypeScript} \\
    \textbf{Deployment \& DevOps}{: App Store Connect, Google Play Console, Fastlane, EAS, GitHub Actions, AWS, Docker}\\
    \textbf{Performance}{: Metro bundler optimization, Code splitting, Image optimization, Native bridge profiling}\\
              \textbf{Leadership}{: Cross‑functional team coordination, Agile/Scrum, Technical mentorship, Code reviews} }}
  }}
\end{itemize}

%------------------ EXPERIENCE ---------------------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Mobile Tech Lead (React Native)}{Jul 2025 –  Current}
    {2Cents Capital}{Bengaluru, India}
    \resumeItemListStart
      \resumeItem{Architected and led development of React Native investment app from ground up, shipping to 10,000+ users on iOS and Android with 95\% on-time feature delivery across 10+ engineers.}
      \resumeItem{Optimized app performance achieving $<$0.5s cold-start time through code splitting, lazy loading, and Metro bundler configuration; reduced bundle size 40\% via tree-shaking and native module integration.}
      \resumeItem{Implemented CI/CD pipeline with Fastlane and GitHub Actions, automating builds, testing, and deployments to TestFlight/Play Console, reducing release cycle from 2 days to 2 hours.}
      \resumeItem{Integrated native modules for biometric authentication, secure storage, and push notifications; built custom bridge for seamless iOS/Android financial SDKs integration.}
      \resumeItem{Established mobile development best practices including TypeScript migration, Jest/Detox testing suite (85\% coverage), and component library achieving 99.9\% crash-free rate.}
    \resumeItemListEnd

  \resumeSubheading
     {Embedded Software Developer}{Jan 2025–Jun 2025}
     {Visteon}{Chennai, India}
    \resumeItemListStart
      \resumeItem{Optimized real-time UI rendering and data processing for automotive dashboards, reducing frame drops 25\% through efficient memory management and event-loop optimization—directly applicable to mobile performance tuning.}
      \resumeItem{Implemented comprehensive test automation achieving 99.8\% code coverage with unit and integration tests; established quality gates preventing regressions in production builds.}
      \resumeItem{Built diagnostic monitoring system processing 1000+ events/second with sub-10ms latency, demonstrating expertise in performance-critical applications.}
    \resumeItemListEnd

  \resumeSubheading
    {Automation Intern}{Dec 2024–Jan 2025}
    {Procter \& Gamble}{Hyderabad, India}
    \resumeItemListStart
      \resumeItem{Built real-time monitoring dashboards processing 2M+ data points daily with 99.9\% uptime, applying responsive design patterns and efficient data visualization techniques.}
      \resumeItem{Developed automated workflows and data-driven interfaces, reducing manual processes 40\% through intuitive UI/UX design.}
    \resumeItemListEnd

  \resumeSubheading
    {IoT \& LoRaWAN Developer}{May 2024–Jun 2024}
    {Tynatech Ingenious Pvt Ltd}{Noida, India}
    \resumeItemListStart
      \resumeItem{Architected RESTful APIs and webhook integrations connecting 50+ IoT devices to cloud platforms, providing robust backend services for mobile/web clients.}
      \resumeItem{Implemented real-time WebSocket/MQTT streaming handling 100+ messages/second, enabling live data visualization in frontend applications.}
    \resumeItemListEnd

  \resumeSubheading
    {Full Stack Developer Intern}{Oct 2023–Dec 2023}
    {Intellect Design Arena}{Chennai, India}
    \resumeItemListStart
      \resumeItem{Optimized web application performance achieving 30\% faster page loads through code splitting, lazy loading, and asset optimization techniques.}
      \resumeItem{Built responsive analytics dashboards with real-time data updates, applying mobile-first design principles for seamless cross-device experience.}
      \resumeItem{Managed cloud deployment and CI/CD pipelines for five applications, ensuring 99.9\% availability through automated testing and monitoring.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%------------------ PROJECTS -----------------------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
    {\textbf{Full‑Stack AI Personal Assistant}
    \( | \) \emph{Go, Google A2A, PostgreSQL, React}}
    {Dec 2024}
\resumeItemListStart
      \resumeItem{Engineered and deployed a cloud assistant that centralizes and automates personal workflows.}
      \resumeItem{Built asynchronous agents to orchestrate complex Google Workspace operations (mail, calendar, docs).}
      \resumeItem{Modeled a personal knowledge graph to ground answers and personalize actions.}
    \resumeItemListEnd
  \resumeProjectHeading
    {\textbf{Instagram Automation Bot}
      \( | \) \emph{Python, FastAPI, Redis, AWS}}{Dec 2024}
    \resumeItemListStart
      \resumeItem{Deployed cloud bot handling 1000+ daily interactions with 99.5\% uptime.}
      \resumeItem{Added LLM‑based sentiment/intent detection achieving 88\% accuracy in production.}
      \resumeItem{Introduced Redis caching to cut Meta Graph API calls 65\%; p50 response <500\,ms.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Multipurpose VR Gloves with Gesture Recognition}
      \( | \) \emph{Unity, C\#, ESP32, ML}}{Sep 2024}
    \resumeItemListStart
      \resumeItem{Built VR gloves capturing 15+ gestures at 92\% accuracy using flex‑sensor ML pipelines.}
      \resumeItem{Developed a web UI to map gestures to 20+ system commands; integrated Unity for gaming/assistive control.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{RAK Gateway Configurator}
      \( | \) \emph{Python, Flask, SQL, Bash}}{Jun 2024}
    \resumeItemListStart
      \resumeItem{Created full-stack tool streamlining configuration of RAKwireless LoRaWAN gateways for network admins.}
      \resumeItem{Automated device discovery, credential management, and firmware upgrades.}
    \resumeItemListEnd


  \resumeProjectHeading
    {\textbf{Wearable Jump-Height Measurement Device}
      \( | \) \emph{ESP32, MPU6050, Flask}}{Mar 2024}
    \resumeItemListStart
      \resumeItem{Ankle‑mounted sensor reached \(\pm1\,\text{cm}\) accuracy vs lab force‑plates.}
      \resumeItem{Used Kalman filtering to suppress sensor noise 80\%; built SQLite/Flask analytics dashboard.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{RFID-based Runner Tracking System}
      \( | \) \emph{Industrial RFID, PHP, Raspberry Pi}}{Dec 2023}
    \resumeItemListStart
      \resumeItem{Automated timing for 5km training runs via industrial RFID readers.}
      \resumeItem{Web interface enabled seamless record management and legacy-system integration.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%------------------ EDUCATION ----------------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Vellore Institute of Technology}{Chennai, India}
    {B.Tech. Electronics \& Computer Engineering; GPA: 8.66/10}{2021–2025}
\resumeSubHeadingListEnd

%--------------------------------------------------
\end{document}3
